\documentclass[11pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage[T1]{fontenc}
\renewcommand{\familydefault}{\sfdefault}
\pagenumbering{gobble}

\begin{document}

\noindent
\textbf{\LARGE Deepesh  kawadkar} \\
India •  • \href{mailto:}{{}} \\
\href{{}}{{}}

\section*{Skills}
{{SKILLS}}

\section*{Education}
Here is the Education section in LaTeX bullet format:

\begin{教育}
\item Bachelor of Technology (B.Tech) in Information Technology (CGPA: 7.74/10)
		+ Chameli Devi Group of Institutions | Indore, India (2020 - 2024)
\item 12th Grade (77.6%)
		+ Career Academy | Indore, India (2019 - 2020)
\item 10th Grade (83.0%)
		+ Regal Cambridge Academy | Indore, India (2017 - 2018)
\end{教育}

Note: LaTeX is a markup language, so this code is not meant to be compiled, but rather serves as a formatted representation of the education section.

\section*{Summary}
Here's a rewritten professional Summary section for the Product Manager resume:

\textbackslash{}textbf\textbackslash{}{Summary:\textbackslash{}}

As a highly motivated and detail-oriented Product Manager with a strong foundation in software development, I leverage my technical expertise to drive innovative solutions. With experience in web development, database management, and IoT development, I have a unique ability to understand the needs of both technical and non-technical stakeholders. My passion for collaboration and problem-solving enables me to effectively communicate with cross-functional teams to deliver products that meet customer needs. Proficient in Agile methodologies, cloud computing, and programming languages such as Java, Python, and JavaScript, I am well-equipped to navigate the complexities of product development from concept to launch.

This summary highlights the candidate's:

* Strong technical background and development skills
* Ability to communicate with technical and non-technical stakeholders
* Experience in product development and management
* Familiarity with Agile methodologies and cloud computing
* Proficiency in multiple programming languages

This summary is concise, yet informative, and should appeal to hiring managers looking for a Product Manager with a strong technical foundation.

\section*{Projects}
Here is the rewritten Projects section in LaTeX itemize format:

\section*{PROJECTS}

\begin{itemize}
\item \textbf{Taskify - Task Management System}
  \begin{itemize}
  \item Description: A web-based task management system designed to help users create, organize, and manage projects and tasks efficiently.
  \item Features:
    \begin{itemize}
    \item Allows users to assign tasks to team members based on priority.
    \item Provides an intuitive interface for tracking task progress and managing deadlines.
    \item Enhances collaboration among team members, making workflow management seamless.
    \end{itemize}
  \item Technologies Used: HTML, CSS, JavaScript, Python, Flask, SQLite
  \item Role: Full-stack Development, Backend API Integration, Database Design
  \end{itemize}

\item \textbf{Restrobook - Restaurant Booking Platform}
  \begin{itemize}
  \item Description: A website that helps users find nearby restaurants and book tables directly through the platform.
  \item Features:
    \begin{itemize}
    \item Search functionality to locate restaurants based on location and user preferences.
    \item Integrated booking system for reserving tables at desired restaurants.
    \item Responsive design for seamless access across devices.
    \end{itemize}
  \item Technologies Used: HTML, CSS, JavaScript, Python, Flask, SQLite
  \item Role: Frontend Development, Database Connectivity, User Interface Design
  \end{itemize}
\end{itemize}

I hope this helps! Let me know if you need any further modifications.

\section*{Work Experience}
Here is the rewritten Experience section in LaTeX bullet format:

\begin{document}

\section{Work Experience}

\begin{itemize}
\item \textbf{Intern, Platforma IT Solutions Pvt Lt, August 2023}
	+ Focused on frontend development and IoT solutions using HTML, CSS, Java, JSP, Arduino, and ESP32.
	+ Designed responsive web interfaces and developed IoT modules for remote monitoring and control.

\item \textbf{Online Internship, IIT Indore, January 2022}
	+ Developed and optimized a perceptron neural network for classifying odd numbers.
	+ Enhanced model accuracy through data preprocessing and hyperparameter tuning while gaining hands-on experience in neural network fundamentals.
\end{itemize}

\end{document}

Note that I used the `itemize` environment to create a bulleted list with two items, each representing a work experience. I also used `\textbf` to bold the company names and descriptions to make them standout. You can adjust the formatting as needed to fit your specific needs.

\end{document}
